---
title: "CRQA HRV pairwise Pro"
output: html_document
date: "2024-05-02"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r results='hide', message=FALSE, warning=FALSE}
library(viridis)
library(crqa)
library(readr)
library(pracma)
library(tseriesChaos)
library(nonlinearTseries)

```

## RQA on HRV for Pro Players

for general justification of using the crqa package for aRQA we looked at e.g.:  https://dl.acm.org/doi/fullHtml/10.1145/3576050.3576113#BibPLXBIB0009 

```{r}

# Pro players 
setwd('C:/Users/jette/Documents/Uni/Tilburg/Semester2/Complex Systems/Project CS/HRV_GSR_Final/HRV/pros/match_10')

Pro0 <- read.csv(file="match_10_player_0.csv")
Pro1 <- read.csv(file="match_10_player_1.csv")
Pro2 <- read.csv(file="match_10_player_2.csv")
Pro3 <- read.csv(file="match_10_player_3.csv")
Pro4 <- read.csv(file="match_10_player_4.csv")

players <- list(Pro0, Pro1, Pro2, Pro3, Pro4)

```


## Parameter Estimation for each player's HRV

We need the embedding dimension, the delay,and the radius: since the data is continuous we need to estimate the parameters 

Following the suggestions here: 
https://ieeexplore.ieee.org/document/9447059 
https://www.frontiersin.org/journals/psychology/articles/10.3389/fpsyg.2018.01679/full 

Delay: AMI 
Embedding Dimension: false-nearest-neighbors (alternative from lecture: Cao)
Radius: should give 1-5% recurrence (according to lecture)

https://ieeexplore.ieee.org/document/9447059  on radius selection: 
3) Estimating Threshold Radius (ε): The final parameter to
construct an appropriate RP is to select the threshold radius
(ε). The method proposed by Zbilut et al. [23] was adopted.
Accordingly, Rec was calculated for a range of radius between
0.01, 0.02, . . . , 0.1, 0.2, . . . , 1, 2 . . . , 10, and for all short-term
window sizes adopted in the study. A plot of thresholds vs
recurrence rates was constructed using a log scale as shown
in Figure 2. From the plot, the condition foot-after-noise
was located by observing the point after which there was
gradual and linear rise in the Rec. All window sizes satisfied
the criteria, however, for the window size of 60, valid Rec
only starts at the threshold 0.7 where a steady rise was
observed (indicated by dashed line in the Figure 2). Thus,
to accommodate the smallest window size of 60, a threshold
ε of 0.7 was considered for subsequent analysis. Further, the
corresponding Rec of 0.067 satisfied the suggested nominal
recurrence rate of 0.01 or 1%. 



## Player 0 

```{r}
# get AMI to select delay 
# select a bin size using Sturges' rule (1926)
bin = ceil(1 + log2(nrow(Pro0)))

mutual(Pro0$RMSSD, bin, 50, plot = TRUE)

```

```{r}
# choose delay 

delay_0 = 1

```


FNN seems flawed for this kind of data: https://ieeexplore.ieee.org/document/4148166?arnumber=4148166 probably due to noise

Therefore choose Cao's method for estimating the embedding dimension instead 

```{r}
# Cao, L. (1997). Practical method for determining the minimum embedding dimension of a scalar time series. Physica D: Nonlinear Phenomena, 110(1-2), 43-50.
embeddim_0 = estimateEmbeddingDim(Pro0$RMSSD, time.lag = delay_0, max.embedding.dim = 20)

```


```{r}
print(embeddim_0)

```

## Player 1

```{r}
# get AMI to select delay 
# select a bin size using Sturges' rule (1926)
bin = ceil(1 + log2(nrow(Pro1)))

mutual(Pro1$RMSSD, bin, 50, plot = TRUE)

```

```{r}
# choose delay 

delay_1 = 2

```

```{r}
# Cao, L. (1997). Practical method for determining the minimum embedding dimension of a scalar time series. Physica D: Nonlinear Phenomena, 110(1-2), 43-50.
embeddim_1 = estimateEmbeddingDim(Pro1$RMSSD, time.lag = delay_1, max.embedding.dim = 20)

```

```{r}
print(embeddim_1)

```


## Player 2 

```{r}
# get AMI to select delay 
# select a bin size using Sturges' rule (1926)
bin = ceil(1 + log2(nrow(Pro2)))

mutual(Pro2$RMSSD, bin, 50, plot = TRUE)

```

```{r}
# choose delay 

delay_2 = 2

```

```{r}
# Cao, L. (1997). Practical method for determining the minimum embedding dimension of a scalar time series. Physica D: Nonlinear Phenomena, 110(1-2), 43-50.
embeddim_2 = estimateEmbeddingDim(Pro2$RMSSD, time.lag = delay_2, max.embedding.dim = 20)

```

```{r}
print(embeddim_2)

```


## Player 3 

```{r}
# get AMI to select delay 
# select a bin size using Sturges' rule (1926)
bin = ceil(1 + log2(nrow(Pro3)))

mutual(Pro3$RMSSD, bin, 50, plot = TRUE)

```

```{r}
# choose delay 

delay_3 = 1

```


```{r}
# Cao, L. (1997). Practical method for determining the minimum embedding dimension of a scalar time series. Physica D: Nonlinear Phenomena, 110(1-2), 43-50.
embeddim_3 = estimateEmbeddingDim(Pro3$RMSSD, time.lag = delay_3, max.embedding.dim = 20)

```

```{r}
print(embeddim_3)

```


## Player 4 

```{r}
# get AMI to select delay 
# select a bin size using Sturges' rule (1926)
bin = ceil(1 + log2(nrow(Pro4)))

mutual(Pro4$RMSSD, bin, 50, plot = TRUE)

```

```{r}
# choose delay 

delay_4 = 1

```

```{r}
# Cao, L. (1997). Practical method for determining the minimum embedding dimension of a scalar time series. Physica D: Nonlinear Phenomena, 110(1-2), 43-50.
embeddim_4 = estimateEmbeddingDim(Pro4$RMSSD, time.lag = delay_4, max.embedding.dim = 20)

```

```{r}
print(embeddim_4)

```

### Choose one set of parameters for all players 
Players 0 - 4 are all pretty similar in terms of their estimated delays and embeddims 
simply take their mean as parameters

```{r}

delay = mean(c(delay_0, delay_1, delay_2, delay_3, delay_4)) 
embeddim =  mean(c(embeddim_0, embeddim_1, embeddim_2, embeddim_3, embeddim_4)) 

print(delay)
print(embeddim)

```
Start with an arbitrary radius of 0.3 -- too low, put up to 0.4

```{r}
radius = 0.4
```

## Get the RQA plots
Fill in the estimated embedding dimension and lag - radius should be chosen so that the RR is around 1-5% 
Try different radii between 0.01 & 10 !!! 
According to e.g. Wallot & Leonardi (2018) a single set of parameters that fits all samples should be found in order to properly compare between all of them. 

### Player 0 vs. 1

```{r, fig.width = 16, fig.height = 10}


RQA.p01 = crqa(ts1 = Pro0$RMSSD,
               ts2 = Pro1$RMSSD,
               delay = delay,
               embed = embeddim,
               rescale = 1,
               radius = radius,
               normalize = 0,
               mindiagline = 2,
               minvertline = 2,
               tw = 0,
               whiteline = FALSE,
               recpt = FALSE)

round(unlist(RQA.p01[1:9]), digit = 2)


```

RR: The percentage of recurrent points falling within the specified radius (range between 0 and 100)
DET: Proportion of recurrent points forming diagonal line structures.
NRLINE: The total number of lines in the recurrent plot
maxL: The length of the longest diagonal line segment in the plot, excluding the main diagonal
L: The average length of line structures
ENTR: Shannon information entropy of diagonal line lengths longer than the minimum length
rENTR: Entropy measure normalized by the number of lines observed in the plot. Handy to compare across contexts and conditions
LAM: Proportion of recurrent points forming vertical line structures
TT: The average length of vertical line structures


```{r}
# safe and convert into numeric matrix for plotting 
ARP = RQA.p01$RP
ARP = matrix(as.numeric(ARP), nrow(ARP))
```


```{r, fig.width = 16, fig.height = 10}
# use the standard plotting function
plotRP(ARP, 
       labelx = "Time in Windows of 15 sec", 
       labely = "Time in Windows of 15 sec", 
       labelmain = "HRV Pro 0 & Pro 1 CRP",
       cols = viridis(50), 
       pcex = 0.75,
       pch = 20,
       show_ticks = TRUE, 
       unit = 250)

```
```{r}
# make a diagonal recurrence profile 

# choose an important time range for the lag around the LoS: 120 seconds (divided by 15 = 8)
windowsize = 8

rescale =  1; 
normalize = 0; 
minvertline = 2; 
mindiagline = 2; 
whiteline = FALSE;
recpt = FALSE; 
tw = 0

res = drpfromts(Pro0$RMSSD, Pro1$RMSSD, windowsize, radius, delay, embeddim, rescale, normalize, mindiagline, minvertline, tw, whiteline, recpt, side = 'both', method = 'crqa', metric = 'euclidean', datatype = 'continuous')

profile = res$profile

plot(-windowsize:windowsize, profile, type = "l", lwd = 5, xlab = "Lags around Line of Synchrony", ylab = "%REC", main = "HRV Pro 0 & Pro 1 Diagonal Recurrence Profile")


```


### Player 0 vs. Player 2 

```{r, fig.width = 16, fig.height = 10}

# do cRQA on the ts itself and thereby do aRQA
RQA.p02 = crqa(ts1 = Pro0$RMSSD,
               ts2 = Pro2$RMSSD,
               delay = delay,
               embed = embeddim,
               rescale = 1,
               radius = radius,
               normalize = 0,
               mindiagline = 2,
               minvertline = 2,
               tw = 0,
               whiteline = FALSE,
               recpt = FALSE)

round(unlist(RQA.p02[1:9]), digit = 2)


```

RR: The percentage of recurrent points falling within the specified radius (range between 0 and 100)
DET: Proportion of recurrent points forming diagonal line structures.
NRLINE: The total number of lines in the recurrent plot
maxL: The length of the longest diagonal line segment in the plot, excluding the main diagonal
L: The average length of line structures
ENTR: Shannon information entropy of diagonal line lengths longer than the minimum length
rENTR: Entropy measure normalized by the number of lines observed in the plot. Handy to compare across contexts and conditions
LAM: Proportion of recurrent points forming vertical line structures
TT: The average length of vertical line structures


```{r}
# safe and convert into numeric matrix for plotting 
ARP = RQA.p02$RP
ARP = matrix(as.numeric(ARP), nrow(ARP))
```


```{r, fig.width = 16, fig.height = 10}
# use the standard plotting function
plotRP(ARP, 
       labelx = "Time in Windows of 15 sec", 
       labely = "Time in Windows of 15 sec", 
       labelmain = "HRV Pro 0 & Pro 2 CRP",
       cols = viridis(50), 
       pcex = 0.75,
       pch = 20,
       show_ticks = TRUE, 
       unit = 250)

```

```{r}
# make a diagonal recurrence profile 

# choose an important time range for the lag around the LoS: 120 seconds (divided by 15 = 8)
windowsize = 8

rescale =  1; 
normalize = 0; 
minvertline = 2; 
mindiagline = 2; 
whiteline = FALSE;
recpt = FALSE; 
tw = 0

res = drpfromts(Pro0$RMSSD, Pro2$RMSSD, windowsize, radius, delay, embeddim, rescale, normalize, mindiagline, minvertline, tw, whiteline, recpt, side = 'both', method = 'crqa', metric = 'euclidean', datatype = 'continuous')

profile = res$profile

plot(-windowsize:windowsize, profile, type = "l", lwd = 5, xlab = "Lags around Line of Synchrony", ylab = "%REC", main = "HRV Pro 0 & Pro 2 Diagonal Recurrence Profile")


```

### Player 0 vs. Player 3

```{r, fig.width = 16, fig.height = 10}

# do cRQA on the ts itself and thereby do aRQA
RQA.p03 = crqa(ts1 = Pro0$RMSSD,
               ts2 = Pro3$RMSSD,
               delay = delay,
               embed = embeddim,
               rescale = 1,
               radius = radius,
               normalize = 0,
               mindiagline = 2,
               minvertline = 2,
               tw = 0,
               whiteline = FALSE,
               recpt = FALSE)

round(unlist(RQA.p03[1:9]), digit = 2)


```

RR: The percentage of recurrent points falling within the specified radius (range between 0 and 100)
DET: Proportion of recurrent points forming diagonal line structures.
NRLINE: The total number of lines in the recurrent plot
maxL: The length of the longest diagonal line segment in the plot, excluding the main diagonal
L: The average length of line structures
ENTR: Shannon information entropy of diagonal line lengths longer than the minimum length
rENTR: Entropy measure normalized by the number of lines observed in the plot. Handy to compare across contexts and conditions
LAM: Proportion of recurrent points forming vertical line structures
TT: The average length of vertical line structures


```{r}
# safe and convert into numeric matrix for plotting 
ARP = RQA.p03$RP
ARP = matrix(as.numeric(ARP), nrow(ARP))
```


```{r, fig.width = 16, fig.height = 10}
# use the standard plotting function
plotRP(ARP, 
       labelx = "Time in Windows of 15 sec", 
       labely = "Time in Windows of 15 sec", 
       labelmain = "HRV Pro 0 & Pro 3 CRP",
       cols = viridis(50), 
       pcex = 0.75,
       pch = 20,
       show_ticks = TRUE, 
       unit = 250)

```

```{r}
# make a diagonal recurrence profile 

# choose an important time range for the lag around the LoS: 120 seconds (divided by 15 = 8)
windowsize = 8

rescale =  1; 
normalize = 0; 
minvertline = 2; 
mindiagline = 2; 
whiteline = FALSE;
recpt = FALSE; 
tw = 0

res = drpfromts(Pro0$RMSSD, Pro3$RMSSD, windowsize, radius, delay, embeddim, rescale, normalize, mindiagline, minvertline, tw, whiteline, recpt, side = 'both', method = 'crqa', metric = 'euclidean', datatype = 'continuous')

profile = res$profile

plot(-windowsize:windowsize, profile, type = "l", lwd = 5, xlab = "Lags around Line of Synchrony", ylab = "%REC", main = "HRV Pro 0 & Pro 3 Diagonal Recurrence Profile")


```

### Player 0 vs. Player 4

```{r, fig.width = 16, fig.height = 10}

# do cRQA on the ts itself and thereby do aRQA
RQA.p04 = crqa(ts1 = Pro0$RMSSD,
               ts2 = Pro4$RMSSD,
               delay = delay,
               embed = embeddim,
               rescale = 1,
               radius = radius,
               normalize = 0,
               mindiagline = 2,
               minvertline = 2,
               tw = 0,
               whiteline = FALSE,
               recpt = FALSE)

round(unlist(RQA.p04[1:9]), digit = 2)


```

RR: The percentage of recurrent points falling within the specified radius (range between 0 and 100)
DET: Proportion of recurrent points forming diagonal line structures.
NRLINE: The total number of lines in the recurrent plot
maxL: The length of the longest diagonal line segment in the plot, excluding the main diagonal
L: The average length of line structures
ENTR: Shannon information entropy of diagonal line lengths longer than the minimum length
rENTR: Entropy measure normalized by the number of lines observed in the plot. Handy to compare across contexts and conditions
LAM: Proportion of recurrent points forming vertical line structures
TT: The average length of vertical line structures


```{r}
# safe and convert into numeric matrix for plotting 
ARP = RQA.p04$RP
ARP = matrix(as.numeric(ARP), nrow(ARP))
```


```{r, fig.width = 16, fig.height = 10}
# use the standard plotting function
plotRP(ARP, 
       labelx = "Time in Windows of 15 sec", 
       labely = "Time in Windows of 15 sec", 
       labelmain = "HRV Pro 0 & Pro 4 CRP",
       cols = viridis(50), 
       pcex = 0.75,
       pch = 20,
       show_ticks = TRUE, 
       unit = 250)

```

```{r}
# make a diagonal recurrence profile 

# choose an important time range for the lag around the LoS: 120 seconds (divided by 15 = 8)
windowsize = 8

rescale =  1; 
normalize = 0; 
minvertline = 2; 
mindiagline = 2; 
whiteline = FALSE;
recpt = FALSE; 
tw = 0

res = drpfromts(Pro0$RMSSD, Pro4$RMSSD, windowsize, radius, delay, embeddim, rescale, normalize, mindiagline, minvertline, tw, whiteline, recpt, side = 'both', method = 'crqa', metric = 'euclidean', datatype = 'continuous')

profile = res$profile

plot(-windowsize:windowsize, profile, type = "l", lwd = 5, xlab = "Lags around Line of Synchrony", ylab = "%REC", main = "HRV Pro 0 & Pro 4 Diagonal Recurrence Profile")


```

### Player 1 vs. Player 2 

```{r, fig.width = 16, fig.height = 10}

# do cRQA on the ts itself and thereby do aRQA
RQA.p12 = crqa(ts1 = Pro1$RMSSD,
               ts2 = Pro2$RMSSD,
               delay = delay,
               embed = embeddim,
               rescale = 1,
               radius = radius,
               normalize = 0,
               mindiagline = 2,
               minvertline = 2,
               tw = 0,
               whiteline = FALSE,
               recpt = FALSE)

round(unlist(RQA.p12[1:9]), digit = 2)


```

RR: The percentage of recurrent points falling within the specified radius (range between 0 and 100)
DET: Proportion of recurrent points forming diagonal line structures.
NRLINE: The total number of lines in the recurrent plot
maxL: The length of the longest diagonal line segment in the plot, excluding the main diagonal
L: The average length of line structures
ENTR: Shannon information entropy of diagonal line lengths longer than the minimum length
rENTR: Entropy measure normalized by the number of lines observed in the plot. Handy to compare across contexts and conditions
LAM: Proportion of recurrent points forming vertical line structures
TT: The average length of vertical line structures


```{r}
# safe and convert into numeric matrix for plotting 
ARP = RQA.p12$RP
ARP = matrix(as.numeric(ARP), nrow(ARP))
```


```{r, fig.width = 16, fig.height = 10}
# use the standard plotting function
plotRP(ARP, 
       labelx = "Time in Windows of 15 sec", 
       labely = "Time in Windows of 15 sec", 
       labelmain = "HRV Pro 1 & Pro 2 CRP",
       cols = viridis(50), 
       pcex = 0.75,
       pch = 20,
       show_ticks = TRUE, 
       unit = 250)

```

```{r}
# make a diagonal recurrence profile 

# choose an important time range for the lag around the LoS: 120 seconds (divided by 15 = 8)
windowsize = 8

rescale =  1; 
normalize = 0; 
minvertline = 2; 
mindiagline = 2; 
whiteline = FALSE;
recpt = FALSE; 
tw = 0

res = drpfromts(Pro1$RMSSD, Pro2$RMSSD, windowsize, radius, delay, embeddim, rescale, normalize, mindiagline, minvertline, tw, whiteline, recpt, side = 'both', method = 'crqa', metric = 'euclidean', datatype = 'continuous')

profile = res$profile

plot(-windowsize:windowsize, profile, type = "l", lwd = 5, xlab = "Lags around Line of Synchrony", ylab = "%REC", main = "HRV Pro 1 & Pro 2 Diagonal Recurrence Profile")


```

### Player 1 vs. Player 3

```{r, fig.width = 16, fig.height = 10}

# do cRQA on the ts itself and thereby do aRQA
RQA.p13 = crqa(ts1 = Pro1$RMSSD,
               ts2 = Pro3$RMSSD,
               delay = delay,
               embed = embeddim,
               rescale = 1,
               radius = radius,
               normalize = 0,
               mindiagline = 2,
               minvertline = 2,
               tw = 0,
               whiteline = FALSE,
               recpt = FALSE)

round(unlist(RQA.p13[1:9]), digit = 2)


```

RR: The percentage of recurrent points falling within the specified radius (range between 0 and 100)
DET: Proportion of recurrent points forming diagonal line structures.
NRLINE: The total number of lines in the recurrent plot
maxL: The length of the longest diagonal line segment in the plot, excluding the main diagonal
L: The average length of line structures
ENTR: Shannon information entropy of diagonal line lengths longer than the minimum length
rENTR: Entropy measure normalized by the number of lines observed in the plot. Handy to compare across contexts and conditions
LAM: Proportion of recurrent points forming vertical line structures
TT: The average length of vertical line structures


```{r}
# safe and convert into numeric matrix for plotting 
ARP = RQA.p13$RP
ARP = matrix(as.numeric(ARP), nrow(ARP))
```


```{r, fig.width = 16, fig.height = 10}
# use the standard plotting function
plotRP(ARP, 
       labelx = "Time in Windows of 15 sec", 
       labely = "Time in Windows of 15 sec", 
       labelmain = "HRV Pro 1 & Pro 3 CRP",
       cols = viridis(50), 
       pcex = 0.75,
       pch = 20,
       show_ticks = TRUE, 
       unit = 250)

```

```{r}
# make a diagonal recurrence profile 

# choose an important time range for the lag around the LoS: 120 seconds (divided by 15 = 8)
windowsize = 8

rescale =  1; 
normalize = 0; 
minvertline = 2; 
mindiagline = 2; 
whiteline = FALSE;
recpt = FALSE; 
tw = 0

res = drpfromts(Pro1$RMSSD, Pro3$RMSSD, windowsize, radius, delay, embeddim, rescale, normalize, mindiagline, minvertline, tw, whiteline, recpt, side = 'both', method = 'crqa', metric = 'euclidean', datatype = 'continuous')

profile = res$profile

plot(-windowsize:windowsize, profile, type = "l", lwd = 5, xlab = "Lags around Line of Synchrony", ylab = "%REC", main = "HRV Pro 1 & Pro 3 Diagonal Recurrence Profile")


```

### Player 1 vs. Player 4

```{r, fig.width = 16, fig.height = 10}

RQA.p14 = crqa(ts1 = Pro1$RMSSD,
               ts2 = Pro4$RMSSD,
               delay = delay,
               embed = embeddim,
               rescale = 1,
               radius = radius,
               normalize = 0,
               mindiagline = 2,
               minvertline = 2,
               tw = 0,
               whiteline = FALSE,
               recpt = FALSE)

round(unlist(RQA.p14[1:9]), digit = 2)


```

RR: The percentage of recurrent points falling within the specified radius (range between 0 and 100)
DET: Proportion of recurrent points forming diagonal line structures.
NRLINE: The total number of lines in the recurrent plot
maxL: The length of the longest diagonal line segment in the plot, excluding the main diagonal
L: The average length of line structures
ENTR: Shannon information entropy of diagonal line lengths longer than the minimum length
rENTR: Entropy measure normalized by the number of lines observed in the plot. Handy to compare across contexts and conditions
LAM: Proportion of recurrent points forming vertical line structures
TT: The average length of vertical line structures


```{r}
# safe and convert into numeric matrix for plotting 
ARP = RQA.p14$RP
ARP = matrix(as.numeric(ARP), nrow(ARP))
```


```{r, fig.width = 16, fig.height = 10}
# use the standard plotting function
plotRP(ARP, 
       labelx = "Time in Windows of 15 sec", 
       labely = "Time in Windows of 15 sec", 
       labelmain = "HRV Pro 1 & Pro 4 CRP",
       cols = viridis(50), 
       pcex = 0.75,
       pch = 20,
       show_ticks = TRUE, 
       unit = 250)

```

```{r}
# make a diagonal recurrence profile 

# choose an important time range for the lag around the LoS: 120 seconds (divided by 15 = 8)
windowsize = 8

rescale =  1; 
normalize = 0; 
minvertline = 2; 
mindiagline = 2; 
whiteline = FALSE;
recpt = FALSE; 
tw = 0

res = drpfromts(Pro1$RMSSD, Pro4$RMSSD, windowsize, radius, delay, embeddim, rescale, normalize, mindiagline, minvertline, tw, whiteline, recpt, side = 'both', method = 'crqa', metric = 'euclidean', datatype = 'continuous')

profile = res$profile

plot(-windowsize:windowsize, profile, type = "l", lwd = 5, xlab = "Lags around Line of Synchrony", ylab = "%REC", main = "HRV Pro 1 & Pro 4 Diagonal Recurrence Profile")


```

### Player 2 vs. Player 3 

```{r, fig.width = 16, fig.height = 10}

RQA.p23 = crqa(ts1 = Pro2$RMSSD,
               ts2 = Pro3$RMSSD,
               delay = delay,
               embed = embeddim,
               rescale = 1,
               radius = radius,
               normalize = 0,
               mindiagline = 2,
               minvertline = 2,
               tw = 0,
               whiteline = FALSE,
               recpt = FALSE)

round(unlist(RQA.p23[1:9]), digit = 2)


```

RR: The percentage of recurrent points falling within the specified radius (range between 0 and 100)
DET: Proportion of recurrent points forming diagonal line structures.
NRLINE: The total number of lines in the recurrent plot
maxL: The length of the longest diagonal line segment in the plot, excluding the main diagonal
L: The average length of line structures
ENTR: Shannon information entropy of diagonal line lengths longer than the minimum length
rENTR: Entropy measure normalized by the number of lines observed in the plot. Handy to compare across contexts and conditions
LAM: Proportion of recurrent points forming vertical line structures
TT: The average length of vertical line structures


```{r}
# safe and convert into numeric matrix for plotting 
ARP = RQA.p23$RP
ARP = matrix(as.numeric(ARP), nrow(ARP))
```


```{r, fig.width = 16, fig.height = 10}
# use the standard plotting function
plotRP(ARP, 
       labelx = "Time in Windows of 15 sec", 
       labely = "Time in Windows of 15 sec", 
       labelmain = "HRV Pro 2 & Pro 3 CRP",
       cols = viridis(50), 
       pcex = 0.75,
       pch = 20,
       show_ticks = TRUE, 
       unit = 250)

```

```{r}
# make a diagonal recurrence profile 

# choose an important time range for the lag around the LoS: 120 seconds (divided by 15 = 8)
windowsize = 8

rescale =  1; 
normalize = 0; 
minvertline = 2; 
mindiagline = 2; 
whiteline = FALSE;
recpt = FALSE; 
tw = 0

res = drpfromts(Pro2$RMSSD, Pro3$RMSSD, windowsize, radius, delay, embeddim, rescale, normalize, mindiagline, minvertline, tw, whiteline, recpt, side = 'both', method = 'crqa', metric = 'euclidean', datatype = 'continuous')

profile = res$profile

plot(-windowsize:windowsize, profile, type = "l", lwd = 5, xlab = "Lags around Line of Synchrony", ylab = "%REC", main = "HRV Pro 2 & Pro 3 Diagonal Recurrence Profile")


```


### Player 2 vs. Player 4

```{r, fig.width = 16, fig.height = 10}

RQA.p24 = crqa(ts1 = Pro2$RMSSD,
               ts2 = Pro4$RMSSD,
               delay = delay,
               embed = embeddim,
               rescale = 1,
               radius = radius,
               normalize = 0,
               mindiagline = 2,
               minvertline = 2,
               tw = 0,
               whiteline = FALSE,
               recpt = FALSE)

round(unlist(RQA.p24[1:9]), digit = 2)


```

RR: The percentage of recurrent points falling within the specified radius (range between 0 and 100)
DET: Proportion of recurrent points forming diagonal line structures.
NRLINE: The total number of lines in the recurrent plot
maxL: The length of the longest diagonal line segment in the plot, excluding the main diagonal
L: The average length of line structures
ENTR: Shannon information entropy of diagonal line lengths longer than the minimum length
rENTR: Entropy measure normalized by the number of lines observed in the plot. Handy to compare across contexts and conditions
LAM: Proportion of recurrent points forming vertical line structures
TT: The average length of vertical line structures


```{r}
# safe and convert into numeric matrix for plotting 
ARP = RQA.p24$RP
ARP = matrix(as.numeric(ARP), nrow(ARP))
```


```{r, fig.width = 16, fig.height = 10}
# use the standard plotting function
plotRP(ARP, 
       labelx = "Time in Windows of 15 sec", 
       labely = "Time in Windows of 15 sec", 
       labelmain = "HRV Pro 2 & Pro 4 CRP",
       cols = viridis(50), 
       pcex = 0.75,
       pch = 20,
       show_ticks = TRUE, 
       unit = 250)

```

```{r}
# make a diagonal recurrence profile 

# choose an important time range for the lag around the LoS: 120 seconds (divided by 15 = 8)
windowsize = 8

rescale =  1; 
normalize = 0; 
minvertline = 2; 
mindiagline = 2; 
whiteline = FALSE;
recpt = FALSE; 
tw = 0

res = drpfromts(Pro2$RMSSD, Pro4$RMSSD, windowsize, radius, delay, embeddim, rescale, normalize, mindiagline, minvertline, tw, whiteline, recpt, side = 'both', method = 'crqa', metric = 'euclidean', datatype = 'continuous')

profile = res$profile

plot(-windowsize:windowsize, profile, type = "l", lwd = 5, xlab = "Lags around Line of Synchrony", ylab = "%REC", main = "HRV Pro 2 & Pro 4 Diagonal Recurrence Profile")


```

### Player 3 vs. Player 4

```{r, fig.width = 16, fig.height = 10}

RQA.p34 = crqa(ts1 = Pro3$RMSSD,
               ts2 = Pro4$RMSSD,
               delay = delay,
               embed = embeddim,
               rescale = 1,
               radius = radius,
               normalize = 0,
               mindiagline = 2,
               minvertline = 2,
               tw = 0,
               whiteline = FALSE,
               recpt = FALSE)

round(unlist(RQA.p34[1:9]), digit = 2)


```

RR: The percentage of recurrent points falling within the specified radius (range between 0 and 100)
DET: Proportion of recurrent points forming diagonal line structures.
NRLINE: The total number of lines in the recurrent plot
maxL: The length of the longest diagonal line segment in the plot, excluding the main diagonal
L: The average length of line structures
ENTR: Shannon information entropy of diagonal line lengths longer than the minimum length
rENTR: Entropy measure normalized by the number of lines observed in the plot. Handy to compare across contexts and conditions
LAM: Proportion of recurrent points forming vertical line structures
TT: The average length of vertical line structures


```{r}
# safe and convert into numeric matrix for plotting 
ARP = RQA.p34$RP
ARP = matrix(as.numeric(ARP), nrow(ARP))
```


```{r, fig.width = 16, fig.height = 10}
# use the standard plotting function
plotRP(ARP, 
       labelx = "Time in Windows of 15 sec", 
       labely = "Time in Windows of 15 sec", 
       labelmain = "HRV Pro 3 & Pro 4 CRP",
       cols = viridis(50), 
       pcex = 0.75,
       pch = 20,
       show_ticks = TRUE, 
       unit = 250)

```

```{r}
# make a diagonal recurrence profile 

# choose an important time range for the lag around the LoS: 120 seconds (divided by 15 = 8)
windowsize = 8

rescale =  1; 
normalize = 0; 
minvertline = 2; 
mindiagline = 2; 
whiteline = FALSE;
recpt = FALSE; 
tw = 0

res = drpfromts(Pro3$RMSSD, Pro4$RMSSD, windowsize, radius, delay, embeddim, rescale, normalize, mindiagline, minvertline, tw, whiteline, recpt, side = 'both', method = 'crqa', metric = 'euclidean', datatype = 'continuous')

profile = res$profile

plot(-windowsize:windowsize, profile, type = "l", lwd = 5, xlab = "Lags around Line of Synchrony", ylab = "%REC", main = "HRV Pro 3 & Pro 4 Diagonal Recurrence Profile")


```

## Get the MdRQA for all five players 
following the instructions in the paper we can embed the five-dimensional time series once at the estimated average delay we selected above to get a 10-dimensional phase space that is quite well in line with the embedding dimensions we estimated before (slightly higher embedding dim according to Wallot and Leonardi 2018 okay) 
```{r}
  
delay = delay; embed = 2; rescale = 1; radius = radius;
normalize = 0; mindiagline = 2; minvertline = 2;
tw = 0; whiteline = FALSE; recpt = FALSE; side = "both"
method = 'mdcrqa'; metric = 'euclidean';  
datatype = "continuous"

all_players <- as.matrix(cbind(Pro0$RMSSD, Pro1$RMSSD, Pro2$RMSSD, Pro3$RMSSD, Pro4$RMSSD))

mdrqa5_results <- crqa(all_players, all_players, delay, embed, rescale, radius, normalize, 
           mindiagline, minvertline, tw, whiteline, recpt, side, method,
           metric, datatype)

round(unlist(mdrqa5_results[1:9]), digit = 2)
```

```{r}
# safe and convert into numeric matrix for plotting 
MdRP = mdrqa5_results$RP
MdRP = matrix(as.numeric(MdRP), nrow(MdRP))
```


```{r, fig.width = 16, fig.height = 10}
# use the standard plotting function
plotRP(MdRP, 
       labelx = "Time in Windows of 15 sec", 
       labely = "Time in Windows of 15 sec", 
       labelmain = "HRV all Pros",
       cols = viridis(50), 
       pcex = 0.75,
       pch = 20,
       show_ticks = TRUE, 
       unit = 250)

```
